A Plasma Torus Around a Young Low-Mass Star

### 2025-01-22 paper/ms.tex
update

{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15,
21, 41, 48, and 75.  Two-minute data were acquired during Sectors
41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute
cadence, which significantly phase-smears sharp features over the
$<$4\,hour period (see \cite{Gunther2022}).  The nearest known star,
TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and based on
the pixel-level TESS data is photometrically stable.

Figure~\ref{fig:fulllc} shows the simple aperture photometry from
Sector~75, which were acquired using the camera that points closest
to the ecliptic.  The largest gap in coverage is from BTJD
3356.0~-~3358.5, and includes the Keck/HIRES observation epoch
(green bar).   There are no flux measurements reported during this
interval because the Earth was within 25$\^circ$ the camera's
boresight, yielding high levels of scattered light.  From BTJD
3359.4~-~3362.0, the Moon also passed within 25$^\circ$ of the
camera's boresight.  Based on the observed level of scattered light
in the local aperture of TIC~141146667, we therefore manually masked
out times from 3359.4~-~3360.13, and judged the remainder of the
data to be usable.  The small data gaps from BTJD 3353.55~-3353.77
and from BTJD 3360.12~-~3360.33 were caused by data downlinks at the
spacecraft's perigee and apogee, respectively.

{\it Keck/HIRES:}
We observed TIC~141146667 ($V$=16.2) with HIRES for five hours over a
second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
16:13.  The star's airmass over this window spanned $z$=1.2-2.2, and
we opted for a fixed 15 minute cadence over the entire sequence,
except for a final 10 minute exposure due to increasing sky
brightness at sunrise.  We observed without the iodine cell and used
the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the red instrument
configuration, yielding a spectral resolution $R$$\approx$45{,}0000
($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
in the spatial dimension, yielding $\approx$1,000 counts (S/N=33)
per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
winds contributed to 1\farcs2$\pm$0\farcs2 seeing over the night,
but conditions were otherwise favorable.  We reduced the
echelleogram to a one-dimensional spectrum using the standard
techniques of the California Planet Survey \cite{Howard2010}.
Figure~\ref{fig:spec} shows a small segment of the result without
any additional processing.

@@

The full wavelength coverage spans 3650-7960\,\AA, and variable
  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.

@@

\subsection{Stellar Parameters}
{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is one of the exceptions.  We calculated the probability
of TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
it appears to be a field star at $>$99.9\% confidence.  Searching the
local vicinity of the star for neighbors with similar projected on-sky
velocity \cite{Tofflemire2021} similarly yields no strong candidates
for co-moving ($\Delta v__{\rm T}$$<$5\,\kms) stars that share its
isochronal youth.

>>>>

{\it Photometry:} TESS observed
TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48, and 75.
Two-minute data were acquired during Sectors 41, 48 (TESS DDT039,
PI: Kunimoto), and 75 (TESS Program G06030, PI: Bouma).  The data
from Sectors 14, 15, and 21 had a 30-minute cadence, which
smears sharp features over the $<$4\,hour period
(see \cite{Gunther2022}).  The nearest known star, TIC~141146666
($T$=14.5), is 25$''$ from TIC~141146667 and is photometrically stable
in the pixel-level TESS data.

Figure~\ref{fig:fulllc} shows the data from Sector~75, which were
acquired using the camera that points closest to the ecliptic.  The
largest gap in coverage is from BTJD 3356.0~-~3358.5, and includes
the Keck/HIRES observation epoch (green bar).   There are no flux
measurements reported during this interval because the Earth was
within 25$^\circ$ the camera's boresight, yielding high levels of
scattered light.  From BTJD 3359.4~-~3362.0, the Moon then passed
within 25$^\circ$ of the camera's boresight.  Based on the observed
level of scattered light in the optimal TIC~141146667 aperture, we
manually masked out times from 3359.4~-~3360.13, and judged the
remainder of the data during the lunar approach to be usable.  The
small data gaps from BTJD 3353.55~-~3353.77 and from BTJD
3360.12~-~3360.33 were caused by data downlinks at the spacecraft's
perigee and apogee, respectively.

{\it Spectroscopy:}
We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours over a
second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
16:13.  The star's airmass over this window spanned $z$=1.2-2.2, and
we opted for a fixed 15 minute cadence over the entire sequence,
except for a final 10 minute exposure due to increasing sky
brightness at sunrise.  We observed without the iodine cell and used
the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the red instrument
configuration, yielding a spectral resolution $R$$\approx$45{,}0000
($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
in the spatial dimension, yielding $\approx$1,000 photons (S/N=33)
per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
winds contributed to 1\farcs2$\pm$0\farcs2 seeing over the night,
but conditions were otherwise favorable.  We reduced the
echelleogram to a one-dimensional spectrum using the standard
techniques of the California Planet Survey \cite{Howard2010}.
Figure~\ref{fig:spec} shows the result in the vicinity of H$\alpha$
without any additional processing.

@@

The full HIRES coverage spans 3650-7960\,\AA, and variable
  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.

@@

\subsection{Stellar Parameters}

{\it Radial Velocity}---We measured the radial velocities of
TIC~141146667 using a pipeline that we for rapidly rotating
stars, including M dwarfs.
%TODO: describe

Standard precision radial velocity pipelines
fail on stars like  due to their extreme line broadening.

{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is one of the exceptions.  We calculated the probability
of TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
it appears to be a field star at $>$99.9\% confidence.  Searching the
local vicinity of the star for neighbors with similar projected on-sky
velocity \cite{Tofflemire2021} similarly yields no strong candidates
for co-moving ($\Delta v_{\rm T}$$<$5\,\kms) stars that share its
isochronal youth.
